Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-24 doc/paper.Rmd
mini change to structure
added table with aoas single feature error rates, outline added

# Introduction and Background

## Motivation
Same-source analyses are a major part of a Forensic Toolmark Examiner's job. In current practice, examiners  make these comparisons by visual inspection under a comparison microscope and come to one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \citep{afte-toolmarks1998}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \citep{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \citep{afte-toolmarks1998}. Potential subject bias in the assessment as well as the lack of specified error rates are the main points of criticisms  first raised by the National Research Council in 2009 \citep{NAS:2009} and later emphasized further by the President's Council of Advisors on Science and Technology \citep{pcast2016}.

@@

@@

\hh{What are we investigating in this paper, and what is the structure for the paper?}

>>>>

# Introduction

Same-source analyses are a major part of a Forensic Toolmark Examiner's job. In current practice, examiners  make these comparisons by visual inspection under a comparison microscope and come to one of the following four conclusions: identification, inconclusive, elimination or unsuitable for examination \citep{afte-toolmarks1998}. These conclusions are made on the basis of "unique surface contours" of the two toolmarks being in "sufficient agreement" \citep{afte-toolmarks1998}. AFTE describes the term "sufficient agreement" as the possibility of another tool producing the markings under comparison, as practically impossible \citep{afte-toolmarks1998}. Potential subject bias in the assessment as well as the lack of specified error rates are the main points of criticisms  first raised by the National Research Council in 2009 \citep{NAS:2009} and later emphasized further by the President's Council of Advisors on Science and Technology \citep{pcast2016}.

@@

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \resizebox{\textwidth}{!}{\begin{tabular}{rlrrr} -->
<!--   \hline -->
<!-- Research paper & Method & Data Source & False Positives & False Negatives\\ -->
<!--   \hline -->
<!--  \textbf{\citet{aoas}} & Consecutive Matching & Bullets & & \\ & Striae (CMS) &  & 6.25\% &  33.851\% \\ \hline -->
<!--  \textbf{\citet{aoas}} & Consecutive Non-matching & Screwdrivers & & \\  & striae (CNMS) & & 6.26\% & 35.4166\%  \\ \hline -->
<!--   \textbf{\citet{aoas}} & Average & Bullets  &  & \\ & Distance &  & 6.25\% & 45.833\% \\ \hline  -->
<!--   \textbf{\citet{aoas}} & Cross-correlation & Bullets & & \\  & Function (CCF) & & 6.25\% & 17.7083\%  \\ \hline -->
<!--   \textbf{\citet{aoas}} & Sum of Peaks & Bullets & & \\  & (S) & & 6.25\% &  18.22915\% \\ &  & & -\% &  -\% \\ -->
<!--    \hline -->
<!-- \end{tabular}} -->
<!-- \caption{\label{tab:bullets-ER} Error Rates in same-source bullet analysis reported in the literature.} -->
<!-- \end{table} -->

\begin{table}[ht]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{rlrrr}
  \hline
Method & Data Source & False Positives & False Negatives\\
  \hline
Consecutive Matching Bullets Striae (CMS) & & & \\ \textbf{\citet{aoas}} &  & 6.25\% &  33.851\% \\ \hline
Consecutive Non-matching Striae (CNMS) & Bullets & & \\  \textbf{\citet{aoas}} & & 6.26\% & 35.4166\%  \\ \hline
Average Distance (D) & Bullets  &  & \\ \textbf{\citet{aoas}} & & 6.25\% & 45.833\% \\ \hline 
Cross-correlation Function (CCF) & Bullets & & \\ \textbf{\citet{aoas}}  & & 6.25\% & 17.7083\%  \\ \hline
Sum of Peaks (S) & Bullets  & & \\  \textbf{\citet{aoas}} & & 6.25\% &  18.22915\% \\
   \hline
\end{tabular}}
\caption{\label{tab:bullets-ER} Error Rates in same-source bullet analysis reported in the literature.}
\end{table}

@@

\hh{What are we investigating in this paper, and what is the structure for the paper?}
\gk{In this paper we evaluate the adaptability of the chumbley score method to bullets, and in the process identify parameters that minimize the error rates. We then identify persistent scenarios in which the method proposed by \citet{hadler} fails to conduct a test. We go on to provide a solution to the failed tests problem, consequently increasing the power of the test and reducing error rates in the process. We also investigate the performance of the two algorithms using higher as well as lower resolution scans to understand if better scans and better equipment have a positive impact on the results.}

# Background
